Modern Graph Generators: A Survey

### 2018-09-02 challenges.tex
Minor corrections, change of order of subsections

In this section, we discuss several of the open challenges in large scale graph
generation.

\subsection{Single- vs. multi-domain}

@@

\subsection{Simple Usage, Simple Parameters}
The proposal of a data generator (not necessarily for graph data) has to face an
important schism. On one hand, it must provide the user with as
many parameters as possible in order to enable him/her to generate
arbitrary data.
This approach seems to be reasonable, but it entails a shortcoming due to
the fact that ordinary users are
unwilling to use complex benchmarking tools. This observation can be
seen, for example, in the case of XML benchmarks -- even though there exist
robust and complex data generators (such as
ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of
structural aspects, value distributions, references etc.), the most popular
benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455}, which models
a single use case and enables to specify just the size of the data. Hence, the
other extreme is to provide a simple data generator which does not require any
complex settings and thus guarantees a simple and fast benchmarking process.

\subsection{Evolving Graph Data}
As user requirements as well as environments change, most of the existing
applications naturally evolve over time, at least to some extent. This evolution
usually influences the structure of the data and consequently all the related
parts of the application (i.e., storage strategies, operations, indexes etc.).
In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}. They can be viewed as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.

@@

The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases. However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a respective generator.

In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e. graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges. The generator generates a time series of random graphs $G_0, G_1, ... G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., the insertion or deletion of an edge or vertex. The generator keeps track of a (dynamic) ground truth clustering. The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.

A recent proposal of a generator~\cite{mlg2018_42} of temporal graphs results from the observation that small subgraph patterns in networks, called \emph{network motifs} or \emph{graphlets}, are crucial indicators of the structure and the evolution of the graphs~\cite{Paranjape:2017:MTN:3018661.3018731}. For a given graph $G$ and a predefined ordered list of structural atomic motifs $M$ the generator first computes the distribution of the motifs in the graph. The distribution is then used to generate a synthetic graph with the same features.

@@

\subsection{Multi-model Data}
With the dawn of Big Data and especially its variety aspect, new types of
database management systems have emerged. One of the most interesting ones
are the so-called \emph{multi-model databases} that enable to store and
thus
query across structurally different data. There exist various types of
multi-model systems combining  distinct subsets of Big Data structures,
such as for instance systems that combine graph data with other data models.
For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
implemented on the basis of an object DBMS currently supports graph, document,
key/value, and object models. Such type of DBMSs also needs a specific
benchmarking data generator that would enable
to test new features and analyze efficiency of operations. However, since the
multi-model systems are in the context of Big Data rather new, there exist only
a few benchmarks targeting multi-model DBMSs (such as
Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
with limited capabilities.
Another interesting approach to multi-model data is to adopt a unifying
expressive graph data model, known as property graph data
model~\cite{BFVY18}. Such a model allows to specify multi-edges and list of
properties for the nodes. Synthetic graph generators for property graphs and its
companion standard graph query language~\cite{Angles18,AnglesABBFGLPPS18} are also needed in order to boost
their availability and adoption for different communities.

\subsection{Large scale graphs with realistic structure}

Most of existing graph generators aiming at generating large graphs with realistic
structural characteristics focus principally on reproducing the degree
distribution and the clustering
coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
structural characteristics one might be interested in reproducing for a large
graph, such the diameter, the size of the largest connected component, or the
hierarchical community structure. Graph practitioners are highly interested in knowing
how other high-level structural characteristics affect the performance of graph
queries and graph algorithms. Hence, a compelling open challenge consists
of creating
graph generators that allow to reproduce diverse structural characteristics
of the graphs along with large scale sizes.

\subsection{Machine Learning based graph generation}

With the advent of neural networks and specially generative adversarial networks
(GANs)~\cite{goodfellow2014generative}, several researchers have started to
explore their application to generate graphs. This is the case of
~\cite{kipf2016variational,grover2018graphite,simonovsky2018graphvae,li2018learning,you2018graphrnn},
which present several generative models to generate realistic graphs.  Such
techniques still suffer from several problems. For instance, some of them are
limited to learn from a single
graph~\cite{kipf2016variational,grover2018graphite} or generate small
graphs~\cite{simonovsky2018graphvae,li2018learning,you2018graphrnn}. The
technique proposed in~\cite{you2018graphrnn} is capable of generating graphs
with complex edge dependencies (e.g. community structure) and is not restricted
to graphs of a fixed size. However, there is still in general several open
challenges, including the capability of learning from and generating large graphs comparable
in size to those typically used for benchmarking, and robust generation
techniques with structural guarantees (e.g. degree distribution, clustering
coefficient, etc.).

\subsection{Generating noisy graphs and graphs with anomalies}
Injecting noise and/or anomalies and errors into graphs is crucial for
testing both machine learning algorithms working on this complex data and
data quality techniques aiming at detecting anomalies and repairing graph
data.

\subsection{Streaming Graph Generators}
Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services,
sensor pervasiveness and emerging Internet-of-Things (IoT) applications. These applications generate the data with \emph{high Velocity}, one of the main 3V characteristics of big data applications~\cite{sakr2016big}. In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner. The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect on other important and timely domains such as IoT. Thus, there is a crucial need to tackle this aspect. In addition, graph streaming generators should  consider some specific aspects for the stream processing domains such as the out-of-order handling (late arrivals)~\cite{li2008out} and the variety in the schemas and formats of the different data streaming sources. It is also recommended for the streaming graph generators to support the distributed environment as this is the most common scenario for such type of applications.

>>>>

To conclude the  overview of the state-of-the-art of graph data generation, in this section we discuss several of the open challenges.

\subsection{Simple Usage, simple Parameters}
The proposal of a data generator (not necessarily for graph data) has to face an
important schism. On one hand, it must provide the user with as
many parameters as possible in order to enable him/her to generate
arbitrary data.
This approach seems to be reasonable, but it entails a shortcoming due to
the fact that ordinary users are
unwilling to use complex benchmarking tools. This observation can be
seen, for example, in the case of XML benchmarks -- even though there exist
robust and complex data generators (such as
ToXGene~\cite{conf/webdb/BarbosaMKL02}, which supports specification of
structural aspects, value distributions, references etc.), the most popular
benchmarking tool is XMark~\cite{Schmidt:2002:XBX:1287369.1287455}, which models
a single use case and enables to specify just the size of the data. Hence, the
other extreme is to provide a simple data generator which does not require any
complex settings and thus guarantees a simple and fast benchmarking process.

\subsection{Large Scale Graphs with Realistic Structure}

Most of existing graph generators aiming at generating large graphs with realistic
structural characteristics focus principally on reproducing the degree
distribution and the clustering
coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
structural characteristics one might be interested in reproducing for a large
graph, such as the diameter, the size of the largest connected component, or the
hierarchical community structure. Graph practitioners are highly interested in knowing
how other high-level structural characteristics affect the performance of graph
queries and graph algorithms. Hence, a compelling open challenge consists
of creating
graph generators that allow to reproduce diverse structural characteristics
of the graphs along with large scale sizes.

\subsection{Single- vs. Multi-domain}

@@

\subsection{Generating Noisy Graphs and Graphs with Anomalies}
Injecting noise and/or anomalies and errors into graphs is crucial for
testing both machine learning algorithms working on this complex data and
data quality techniques aiming at detecting anomalies and repairing graph
data.

\subsection{Streaming Graph Generators}
Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services,
sensor pervasiveness and emerging IoT applications. These applications generate the data with high Velocity, one of the main 3V characteristics of big data applications~\cite{sakr2016big}. In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner. The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect in other important and timely domains such as IoT. %Thus, there is a crucial need to tackle this aspect.
In addition, graph streaming generators should  consider some specific aspects for the stream processing domains such as the out-of-order handling (late arrivals)~\cite{li2008out} and the variety in the schemas and formats of the different data streaming sources. It is also recommended for the streaming graph generators to support the distributed environment as this is the most common scenario for such type of applications.

\subsection{Evolving Graph Data}
As user requirements as well as environments change, most of the existing
applications naturally evolve over time, at least to some extent. This evolution
usually influences the structure of the data and consequently all the related
parts of the application (i.e., storage strategies, operations, indexes etc.).
In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}. They can be modelled as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.

@@

The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases. However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a generator dealing with this area. In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e. graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges. The generator generates a time series of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., insertion or deletion of an edge or a vertex. The generator keeps track of a (dynamic) ground truth clustering. The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.

Another recent proposal of a generator~\cite{mlg2018_42} of temporal graphs results from an observation that small subgraph patterns in networks, called \emph{network motifs} or \emph{graphlets}, are crucial indicators of the structure and the evolution of the graphs~\cite{Paranjape:2017:MTN:3018661.3018731}. For a given graph and a predefined ordered list of structural atomic motifs the generator first computes the distribution of the motifs in the graph. The distribution is then used to generate a synthetic graph with the same features.

@@

\subsection{Multi-model Data}
With the dawn of Big Data and especially its variety aspect, new types of
database management systems have emerged. One of the most interesting ones
are the so-called \emph{multi-model databases} that enable to store and
thus query across structurally different data. There exist various types of
multi-model systems combining  distinct subsets of Big Data structures including graph data.
For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
implemented on the basis of an object DBMS currently supports graph, document,
key/value, and object models. Such type of DBMSs also needs a specific
data generator that would enable
to test new features and analyze efficiency of operations. However, since the
multi-model systems are in the context of Big Data rather new, there exist only
a few benchmarks targeting multi-model DBMSs (such as
Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
with limited capabilities.

Another interesting approach to multi-model data is to adopt a unifying
expressive graph data model, known as property graph data
model~\cite{BFVY18}. Such a model allows to specify multi-edges and list of
properties for the nodes. Synthetic graph generators for property graphs and its
companion standard graph query language~\cite{Angles18,AnglesABBFGLPPS18} are also needed in order to boost
their availability and adoption for different communities.

\subsection{Machine Learning Based Graph Generation}

With the advent of neural networks and specially generative adversarial networks
(GANs)~\cite{goodfellow2014generative}, several researchers have started to
explore their application to generate graphs. This is the case of
~\cite{kipf2016variational,grover2018graphite,simonovsky2018graphvae,li2018learning,you2018graphrnn},
which present several generative models to generate realistic graphs.  Such
techniques still suffer from several problems. For instance, some of them are
limited to learn from a single
graph~\cite{kipf2016variational,grover2018graphite} or generate small
graphs~\cite{simonovsky2018graphvae,li2018learning,you2018graphrnn}. The
technique proposed in~\cite{you2018graphrnn} is capable of generating graphs
with complex edge dependencies (e.g. community structure) and is not restricted
to graphs of a fixed size. However, there are still in general several open
challenges, including the capability of learning from and generating large graphs comparable
in size to those typically used for benchmarking, and robust generation
techniques with structural guarantees (e.g. degree distribution, clustering
coefficient, etc.).
